Analysis of the \\ Information Security Job Landscape \\ in Austria

### 2020-05-27 paper/paper.tex
Fix spacing and commit graphs.

@@

@@

\usepackage{float}
\usepackage{graphicx}
\graphicspath{{assets/}}
\usepackage{listings}
\usepackage[hyphens]{url}
\usepackage{hyperref}

@@

\title{Analysis of the \\ Information Security Job Landscape \\ in Austria}

@@

@@

For example, the scraped data from the URL

\url{https://at.indeed.com/rc/clk?jk=db6f5459c93e648c&fccid=1272531993b16790&vjs=3}

would be saved as

\texttt{indeed-43da336235334055a25f32a55e7cd343128905d782cd749349659ca3d3d38174.json}

@@

\begin{table}[h]
	\centering
  \caption{List of extracted certifications.}
  \label{tab:certifications}

@@

Next up we will take a look at the required level of education for information security jobs. As shown in \autoref{fig:education_chart}, the majority of positions -- around 59\% -- require a bachelor's degree while only around 9\% require a master's degree. The second most common requirement is an apprenticeship (Ausbildung) at around 36\%, followed by the Matura with 22\%. After a manual review of the 4\% belonging to apprenticeship (Lehre), these seem to be mostly false positives, at least in our case when only taking information security jobs into account.

@@

The distribution across the states of Austria was another point we wanted to analyse. The vast majority of advertisements are for positions in Vienna at about 57\%. Of the other states, only Carinthia, Styria and Upper Austria manage to pass the 5\% threshold. Tyrol and Salzburg are both at around 4\% and Lower Austria is at less than 1\% of all advertisements. Vorarlberg and Burgenland do not even have one job advertisement listed.

@@

@@

\section{Future Work}
\label{sec:future_work}

>>>>

\linespread{1.1}

\usepackage{lmodern}
\usepackage[english]{babel}

@@

\raggedbottom

@@

\usepackage{float}
\usepackage{graphicx}
\graphicspath{{assets/}}
\usepackage{listings}

\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{nameref}

@@

\title{Analysis of the \texorpdfstring{\\}{} Information Security Job Landscape \texorpdfstring{\\}{} in Austria}

@@

\vspace{8em}

@@

For example, the scraped data from the URL \\
\texttt{https://at.indeed.com/rc/clk?jk=db6f5459c93e648c\&fccid=1272531993b\\16790\&vjs=3} would be saved as
\texttt{indeed-43da336235334055a25f32a55e7cd3431\\28905d782cd749349659ca3d3d38174.json}.

@@

\begin{table}[ht]
	\centering
  \caption{List of extracted certifications.}
  \label{tab:certifications}

@@

Next up we will take a look at the required level of education for information security jobs. As shown in \autoref{fig:education_chart}, the majority of positions -- around 59\% -- require a bachelor's degree while only around 9\% require a master's degree.

@@

The second most common requirement is an apprenticeship (Ausbildung) at around 36\%, followed by the Matura with 22\%. After a manual review of the 4\% belonging to apprenticeship (Lehre), these seem to be mostly false positives, at least in our case when only taking information security jobs into account.

@@

The distribution across the states of Austria was another point we wanted to analyse. The vast majority of advertisements are for positions in Vienna at about 57\%.

Of the other states, only Carinthia, Styria and Upper Austria manage to pass the 5\% threshold. Tyrol and Salzburg are both at around 4\% and Lower Austria is at less than 1\% of all advertisements. Vorarlberg and Burgenland do not even have one job advertisement listed.

@@
